\chapter{Cortex M1 on Xilinx}

Description of the setup of the Cortex M1 core. \cite{arm_arm_2018} \cite{arm_cortex-m1_nodate}

\section{Usage of Cortex M1 in Vivado}

Only global implementation / synthesis runs are permitted to obtain a working bitstream.
If OOC (Out of Context) runs are used, everything except for the Cortex M1 will work fine. 
The Cortex M1 will enter a hard-fault state which does not allow recovery. 
This is indicated by a high bit on the \textit{Lockup} port of the processor.

Also trivial, follow tutorial that is provided on ARM Website and adapt to own needs.

\subsection{Code via Memory Initialization File}

To update the Memory Initialization File for a core, a new package with the updated \textit{bram\_a7.hex} file in the corresponding core (\textit{/cores/cm1\_*/m1\_for\_arty\_a7.srcs/\\sources\_1/imports/m1\_for\_arty\_a7/m1\_for\_arty\_a7/} \cite{fpga_design}) has to be generated and the \gls{IP} in the block design has to be updated.

\section{How to mbed OS}
To achieve a common code base for the application code, Mbed OS, a \gls{RTOS} from ARM, was used (Fig \ref{fig:mbed}). 
Since there is no support for the Xilinx Cortex M1 core, the \gls{BSP} provided by Xilinx was ported to Mbed OS \cite{mbed_port}. 
The port includes the \gls{RTOS} kernel and the GPIO and UART modules. 
The firmware for our \gls{FPGA} design \cite{fpga_design} can be found on GitHub \cite{firmware}. 
For using Mbed OS with a new design, the \gls{BSP} has to be exported from the Vivado SDK and copied to \textit{/mbed-os/targets/TARGET\_Xilinx/TARGET\_XC7Z020/device/standalone\_bsp/} in \cite{firmware}.

\begin{figure}[ht]
    \centering
\begin{tikzpicture}[
    node distance = 7mm and 12mm,% for distance between nodes
       box/.style = {draw, minimum width=12em}% nodes style
    ]
    \node (app) [box] {Application};
    \node (mbed) [box, below=of app.south] {ARM Mbed OS};
    \node (ph) [below=of mbed.south] {};
    \node (xilinx) [box, left=of ph.west] {Xilinx Cortex M1 core};
    \node (stm) [box, right=of ph.east] {STM32 MCU};
    \draw[->] (app) edge (mbed);
    \draw[->] (mbed) edge (xilinx);
    \draw[->] (mbed) edge (stm);
\end{tikzpicture}
\caption{Software structure.}\label{fig:mbed}
\end{figure}

